NLO QCD+EW corrections to diphoton production in association with a vector boson

### 2017-10-30 results.tex
minor corrections to results

The triple photon production process is defined 
by the presence of three identified photons in the 
central detector. 
To this end we use the smooth cone isolation 
criterion \cite{Frixione:1998jh}, limiting the amount of 
hadronic activity in a cone $R_\gamma$ to
\begin{equation}
  \begin{split}
    E_{{\rm had, max}} (r_{\gamma})
    = \epsilon\, \pT^{\gamma} \left( \frac{1-\cos r_\gamma}
				       {1-\cos R_\gamma}\right)^{n}\;,
  \end{split}
  \label{eq:frix}
\end{equation}
where $r_{\gamma}$ denotes the angular separation between the photon and 
the parton, with 
\begin{equation}
  \label{eq:coneparams}
  \begin{split}
    R_{\gamma}=0.4\;, \quad \epsilon = 0.05\;, \quad n = 1\;, 
  \end{split}
\end{equation}
to define isolated photon candidates.
These candidates are then ordered in transverse momentum. 
We then require at least three such candidates within $|\eta|<2.37$, 
the leading one of which needs $\pT>40\,\text{GeV}$, 
while the all subleading ones need only 
$\pT>30\,\text{GeV}$. 
Finally, a pairwise separation of $\Delta R(\gamma_i,\gamma_j)>0.4$ 
between all identified photons is required.
It is worth noting that at NLO EW it is possible to find more 
than three isolated photons, in which case any combination may 
fulfill the above criteria.

@@

Figure \ref{fig:aaa:pt} displays the transverse momenta of the 
first three leading photons. 
The first observation is that, with the chosen set of cuts, 
the leading and subleading photon are of similar hardness, 
and generally much harder than the third leading photon. 
This suggest that we select primarily diphoton production events 
which is accompanied by a third, most bremsstrahlung, photon. 
The NLO QCD corrections exhibit a handful of interesting features. 
In the absence of a jet veto the fixed-order calculation 
exhibits a huge correction factors, mainly induced by the 
opening of new channels in the real emission. 
Similar, kinematic constraints present at LO \footnote{
  At leading order the leading photon needs to be in a different 
  hemisphere than both the subleading and third leading photon. 
  Thus, $\Delta\phi_{\gamma_1\gamma_2}$ and $\Delta\phi_{\gamma_1\gamma_3}$ 
  must be larger that $\tfrac{1}{2}\,\pi$.
} are released and 
lead to a larger phase space that can be populated. 
These findings mandate the inclusion of at least the $\aaa+\text{jet}$ 
production process at NLO QCD to arrive at a reliable description 
of inclusive \aaa\ production, and thus either a NNLO QCD calculation 
or a multijet merging ansatz \cite{Hoeche:2012yf,Kallweit:2015dum}. 
While the inclusive QCD corrections at very small transverse momenta 
are universally large for all three leading photon \pT-spectra 
($\deltaQCD\approx 2$), they remain at exorbitantly large 
($\deltaQCD\approx 1.5$) throughout the considered range 
only for the leading jet \pT. 
For both subleading photons the QCD corrections are quickly 
decreasing, leveling out at a $\approx 20\%$ at large transverse 
momenta.
In the presence of a restrictive jet veto the very low transverse 
momentum region still experiences large correction of about 
$\deltaQCD\approx 1$. 
As transverse momenta are increasing, the QCD corrections now turn 
negative reaching now $-50-60\%$ and for all three photons.

@@

The QCD corrections themselves again exceed $200\%$ at 
small invariant masses, already well before the above 
described kinematic boundary effect takes hold. 
As the invariant masses are increasing, the 
QCD corrections are dropping to $20-30\%$ for the inclusive 
selection. 
The structure the QCD corrections exhibit around 80-90\,GeV 
in all three diphoton-pair invariant masses are induced by 
the acceptance cuts.
In the presence of the jet veto, the QCD corrections are 
reduced and turn negative beyond $m_{\gamma\gamma}\gtrsim 300\,\text{GeV}$ 
reaching around $-40\%$ at 1\,TeV. 
The electroweak corrections, on the other hand, are 
again moderate, ranging from $+1.5\%$ between 70 and 200\,GeV 
for $m_{\gamma_1\gamma_2}$ and $m_{\gamma_1\gamma_2}$ and 
0 and 100\,GeV for $m_{\gamma_2\gamma_3}$. 
$m_{\gamma_1\gamma_2}$ exhibits a small rise in the correction 
at $2m_W$ due to resonant box diagrams in that region. 
This feature is also present in the electroweak corrections 
to diphoton production in this observable \cite{Chiesa:2017gqx}. 
At large transverse momentum the usual Sudakov logarithms 
are recovered, resulting in corrections of around 
$-8\%$ at 1\,TeV for all photon-pair invariant masses. 
Most importantly, beyond $m_{\gamma\gamma}\gtrsim 300\,\text{GeV}$, 
the electroweak corrections are again not covered by the LO 
uncertainty estimate.

@@

Figure \ref{fig:aaw:pt} shows the transverse momenta of 
the leading and subleading photon as well as the charged 
lepton. 
As was observed in triple photon production, the inclusive 
NLO QCD corrections are large. 
Nonetheless, they differ substatially between the three 
oberservables and in their different regions. 
While $\deltaQCD$ rises from values of 0.3 at small 
transverse momenta of the leading photon to 2 at 
$\pT\approx 100\,\text{GeV}$, it remains constant above that 
value.
In the subleading photon's transverse momentum, the 
situation is different. 
Experiencing a cut-induced jump from 0.3 to 2.5 at low \pT, 
it decreases steadily thereafter to reach $\deltaQCD=0.8$ 
at 500\,GeV. 
The behaviour of the QCD corrections to the lepton \pT are 
then again qualitatively similar to that of the leading 
photon, start at $\deltaQCD=0.8$ at low \pT \, and rising 
steeply to 2.5 at 100\,GeV and then gradually leveling out 
at 3.5. 
Again, the presence of a restrictive jet veto has little 
effect on the small transverse momentum regions, but 
effectively contains the size of the NLO QCD corrections 
to remain below $\deltaQCD=0.5$. 
Instead, they are again driven negative, reaching 
$-20-30\%$ for all three observables.

@@

Figure \ref{fig:aaz:myy} continues to display the invariant masses 
of the leading and subleading photon, and both the leading and 
subleading photon and the lepton pair. 
The familiar peak in $m_{\gamma_i\ell^+\ell^-}$ is produced by 
configurations where the respective photon is emitted by the 
lepton-pair from a resonant $Z$ boson decay. 
Again, the QCD corrections are moderate, always staying below 
$\deltaQCD=0.4$ and of a similar shape as encoutered already in 
\aaw\ production. 
The jet veto again reduces the QCD correction and drives in negative 
in large portions of the observable range, reaching as much as 
$\deltaQCD=-0.5$ for the diphoton invariant mass. 
The electroweak corrections, on the other hand, are very similar 
to the \aaw case: with the exception of the well known positive 
radiative corrections below the $Z$ peak, they are negative 
throughout, reaching $\deltaEW=-20\%$ at invariant masses of 
1\,TeV.
As in the case of the transverse momenta, due to the similar size 
of the QCD and electroweak corrections at large transverse 
momenta, the difference between their additive and the multiplicative 
combination is amplified.

@@

In Figure \ref{fig:aaz:dphi} we consider the azimuthal separation 
between the leading and subleading photon, and both the leading 
and subleading photon and the lepton pair.
While the both photons tend to be back-to-back, the azimuthal 
separation of the leading photon and the lepton pair exhibits 
a kinematic edge at LO, restricting it to be larger than 
$\tfrac{1}{2}\,\pi$. 
\comment{MS: Do we understand why this is?}
On the contrary, the azimuthal separation of the subleading 
photon and the lepton pair exhibits no such limit at LO and 
instead peaks at roughly $\Delta\phi=\tfrac{1}{2}\,\pi$. 
The QCD corrections, with the exception of the aforementioned 
edge, are generally flat, taking values of $\deltaQCD\approx 0.3$ 
in the absence and $\deltaQCD\approx 0.2$ in the presence 
of a jet veto. 
The electroweak corrections are equally flat and amount to 
$\deltaEW\approx-4\%$. 
Their additive and multiplicative combinations are very 
similar.

>>>>

The triple photon production process is defined 
by the presence of three identified photons in the 
central detector. 
To this end we use the smooth cone isolation 
criterion \cite{Frixione:1998jh}, limiting the amount of 
hadronic activity in a cone $R_\gamma$ to
\begin{equation}
  \begin{split}
    E_{{\rm had, max}} (r_{\gamma})
    = \epsilon\, \pT^{\gamma} \left( \frac{1-\cos r_\gamma}
				       {1-\cos R_\gamma}\right)^{n}\;,
  \end{split}
  \label{eq:frix}
\end{equation}
where $r_{\gamma}$ denotes the angular separation between the photon and 
the parton, with 
\begin{equation}
  \label{eq:coneparams}
  \begin{split}
    R_{\gamma}=0.4\;, \quad \epsilon = 0.05\;, \quad n = 1\;, 
  \end{split}
\end{equation}
to define isolated photon candidates.
These candidates are then ordered in transverse momentum. 
We require at least three such candidates within $|\eta|<2.37$, 
the leading one of which needs $\pT>40\,\text{GeV}$, 
while the all subleading ones need only 
$\pT>30\,\text{GeV}$. 
Finally, a pairwise separation of $\Delta R(\gamma_i,\gamma_j)>0.4$ 
between all identified photons is required.
It is worth noting that at NLO EW it is possible to find more 
than three isolated photons, in which case any combination may 
fulfill the above criteria.

@@

Figure \ref{fig:aaa:pt} displays the transverse momenta of the 
first three leading photons. 
The first observation is that, with the chosen set of cuts, 
the leading and subleading photon are of similar hardness, 
and generally much harder than the third leading photon. 
This suggest that we select primarily diphoton production events 
which is accompanied by a third, mostly bremsstrahlung, photon. 
The NLO QCD corrections exhibit a handful of interesting features. 
In the absence of a jet veto the fixed-order calculation 
exhibits huge correction factors, mainly induced by the 
opening of new channels in the real emission. 
Additionally, kinematic constraints present at LO \footnote{
  At leading order the leading photon needs to be in a different 
  hemisphere than both the subleading and third leading photon. 
  Thus, $\Delta\phi_{\gamma_1\gamma_2}$ and $\Delta\phi_{\gamma_1\gamma_3}$ 
  must be larger that $\tfrac{1}{2}\,\pi$.
} are released and 
lead to a larger phase space that can be populated. 
These findings mandate the inclusion of at least the $\aaa+\text{jet}$ 
production process at NLO QCD to arrive at a reliable description 
of inclusive \aaa\ production, and thus either a NNLO QCD calculation 
or a multijet merging ansatz \cite{Hoeche:2012yf,Kallweit:2015dum}. 
While the inclusive QCD corrections at very small transverse momenta 
are universally large for all three leading photon \pT-spectra 
($\deltaQCD\approx 2$), they remain at exorbitantly large 
($\deltaQCD\approx 1.5$) throughout the considered range 
only for the leading jet \pT. 
For both subleading photons the QCD corrections are quickly 
decreasing, leveling out at a approximately $20\%$ at large transverse 
momenta.
In the presence of a restrictive jet veto the very low transverse 
momentum region still experiences large correction of about 
$\deltaQCD\approx 1$. 
As transverse momenta are increasing, however, the QCD corrections now turn 
negative reaching now $-50-60\%$ and for all three photons.

@@

The QCD corrections themselves again exceed $200\%$ at 
small invariant masses, already well before the above 
described kinematic boundary effect takes hold. 
As the invariant masses are increasing, the 
QCD corrections are dropping to $20-30\%$ for the inclusive 
selection. 
The structure the QCD corrections exhibit around 80-90\,GeV 
in all three diphoton-pair invariant masses are induced by 
the acceptance cuts.
In the presence of the jet veto, the QCD corrections are 
reduced and turn negative beyond $m_{\gamma\gamma}\gtrsim 300\,\text{GeV}$ 
reaching around $-40\%$ at 1\,TeV. 
The electroweak corrections, on the other hand, are 
again moderate, ranging from $+1.5\%$ between 70 and 200\,GeV 
for $m_{\gamma_1\gamma_2}$ and $m_{\gamma_1\gamma_3}$ and 
0 and 100\,GeV for $m_{\gamma_2\gamma_3}$. 
$m_{\gamma_1\gamma_2}$ exhibits a small rise in the correction 
at $2m_W$ due to resonant box diagrams in that region. 
This feature is also present in the electroweak corrections 
to diphoton production in this observable \cite{Chiesa:2017gqx}. 
At large transverse momentum the usual Sudakov logarithms 
are recovered, resulting in corrections of around 
$-8\%$ at 1\,TeV for all photon-pair invariant masses. 
Most importantly, beyond $m_{\gamma\gamma}\gtrsim 300\,\text{GeV}$, 
the electroweak corrections are again not covered by the LO 
uncertainty estimate.

@@

Figure \ref{fig:aaw:pt} shows the transverse momenta of 
the leading and subleading photon as well as the charged 
lepton. 
As was observed in triple photon production, the inclusive 
NLO QCD corrections are large. 
Nonetheless, they differ substantially between the three 
oberservables and in their different regions. 
While $\deltaQCD$ rises from values of 0.3 at small 
transverse momenta of the leading photon to 2 at 
$\pT\approx 100\,\text{GeV}$, it remains constant above that 
value.
In the subleading photon's transverse momentum, the 
situation is different. 
Experiencing an acceptance cut induced jump from 0.3 to 2.5 at low \pT, 
it decreases steadily thereafter to reach $\deltaQCD=0.8$ 
at 500\,GeV. 
The behaviour of the QCD corrections to the lepton \pT\ are 
then again qualitatively similar to that of the leading 
photon, starting at $\deltaQCD=0.8$ at low \pT \, and rising 
steeply to 2.5 at 100\,GeV and then gradually leveling out 
at 3.5. 
Again, the presence of a restrictive jet veto has little 
effect on the small transverse momentum regions, but 
effectively contains the size of the NLO QCD corrections 
to remain below $\deltaQCD=0.5$. 
Instead, they are again driven negative, reaching 
$-20-30\%$ for all three observables.

@@

Figure \ref{fig:aaz:myy} continues to display the invariant masses 
of the leading and subleading photon, and both the leading and 
subleading photon and the lepton pair. 
The familiar peak in $m_{\gamma_i\ell^+\ell^-}$ is produced by 
configurations where the respective photon is emitted by the 
lepton-pair from a resonant $Z$ boson decay. 
Again, the QCD corrections are moderate, always staying below 
$\deltaQCD=0.4$ and of a similar shape as encoutered already in 
\aaw\ production. 
The jet veto again reduces the QCD corrections and drives them negative 
in large portions of the observable range, reaching as much as 
$\deltaQCD=-0.5$ for the diphoton invariant mass. 
The electroweak corrections, on the other hand, are qualitatively very similar 
to the \aaw case: with the exception of the well known positive 
radiative corrections below the $Z$ peak, they are negative 
throughout, reaching $\deltaEW=-20\%$ at invariant masses of 
1\,TeV.
As in the case of the transverse momenta, due to the similar size 
of the QCD and electroweak corrections at large transverse 
momenta, the difference between their additive and the multiplicative 
combination is amplified.

@@

In Figure \ref{fig:aaz:dphi} we consider the azimuthal separation 
between the leading and subleading photon, and both the leading 
and subleading photon and the lepton pair.
While both photons tend to be back-to-back, the azimuthal 
separation of the leading photon and the lepton pair exhibits 
a kinematic edge at LO, restricting it to be larger than 
$\tfrac{1}{2}\,\pi$. 
\comment{MS: Do we understand why this is?}
On the contrary, the azimuthal separation of the subleading 
photon and the lepton pair exhibits no such limit at LO and 
instead peaks at roughly $\Delta\phi=\tfrac{1}{2}\,\pi$. 
The QCD corrections, with the exception of the aforementioned 
edge, are generally flat, taking values of $\deltaQCD\approx 0.3$ 
in the absence and $\deltaQCD\approx 0.2$ in the presence 
of a jet veto. 
The electroweak corrections are equally flat and amount to 
$\deltaEW\approx-4\%$. 
Their additive and multiplicative combinations are very 
similar.
